Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-27 main.tex
Tweaks on safety

>>>>

\rb{New try. Contours are as above.}

A {\em call/return map} $\kappa \in \WORDS \rightarrow \{\CRCALL, \CRRET,
\CRBOT\}$ is a map from addresses to tags (not to be confused with tags at the
micropolicy level \rb{reference if needed}) that denote whether a memory
location is to be treated as (the first word of) a call instruction, a return
instruction, or neither \rb{(and we should compare these with call and return
machine instructions ``proper'')}.

The {\em step relation} $(\stepkappa) :: \MACHS \rightharpoonup \MACHS$ is a
partial function from machine states to machine states: a restriction of the
native machine's step relation $\stepstounderfull$ indexed by a call/return
map $\kappa$, such that \rb{(How much to build into this, and/or the machine
states themselves? Also describe and notate the concept of ``running until
the first unmatched return (cf. observable halting states)'') \ldots}

Given a machine state $\mach$ and associated contour $\contour$, an
$\ACCNO$-variant is any state $\mach'$ that varies machine components tagged as
$\ACCNO$ in $\mach$: that is, for any component $\component$ of $\mach$, if
$\contour(\component) \neq \ACCNO$, then
$\mach(\component) = \mach'(\component)$; otherwise (if
$\contour(\component) = \ACCNO$), then $\mach'(\component)$ holds an
arbitrary value, unrelated to $\mach(\component)$. Similarly, $\ACCYES$-variant
states are defined by scrambling those machine components tagged as $\ACCYES$
and leaving all others unchanged.

A machine state $\mach$ is {\em safe} with respect to a contour $\contour$
\rb{and call/return map $\kappa$} if it satisfies the following conditions:
%
\begin{enumerate}

\item {\em Integrity:} if we run $\mach$ until its first unmatched return (if
  any), all components other than those marked as accessible must remain
  unchanged with respect to $\mach$. \rb{That is, the final state is an
  $\ACCYES$-variant of $\mach$.}

\item {\em Confidentiality:} for every $\ACCNO$-variant $\mach'$ of $\mach$, if
  we run $\mach$ and $\mach'$ until their first unmatched returns, the resulting
  final states are themselves $\ACCNO$-variant of one another. \rb{(Homogenize
  notations, see also above.)}

\item Let $\mach_1, \mach_2, \ldots$ be a machine execution starting from
  $\mach$, i.e., $\mach_1 = \mach$. Let also $\contour_1, \contour_2, \ldots$
  be the corresponding sequence of contours, such that $\contour_1 = \contour$
  and at each step $\mach_i$ the corresponding $\contour_i$ \rb{\ldots better
  define the contour-updating step in the style of $\stepplus$.} For all $i$,
  if $M_i$ is a top-level call in the trace, then (the instruction immediately
  after) it \rb{$\mach_{i+1}$?} is safe with respect to $C_i$.

\item All instructions executed throughout any run starting from $\mach$ are
  marked as such in the contour $\contour$. \rb{Need notation to dereference the
  PC and have the memory be marked as $\ACCCODE$:
  $\contour_i(\PC{\mach_i}) = \ACCCODE$ (or noting invariance in $\ACCCODE$
  parts of $\contour$).}

\end{enumerate}

The step relation $\stepkappa$ is itself safe if every machine state $\mach$ is
safe with respect to the special contour where all memory locations containing
code are marked $\ACCCODE$ and all other components are marked $\ACCYES$.
